---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `gnrprod`

`gnrprod` implements the nonparametric identification of gross output production functions outlined in Gandhi, Navarro, and Rivers (2020). The main wrapper function `gnrprod` estimates the parameters of production functions and productivity. At the moment, this function supports only one flexible input.

## Installation

To install the latest development version of \code{gnrprod} from Github, run the following from R:

``` r
install.packages("devtools")
library(devtools)
devtools::install_github("davidjin0/gnrprod")
library(gnrprod)
```

## Usage

This package features three main functions: `gnrprod`, `gnrflex`, and `gnriv`. `gnrprod` performs the entire production function estimation routine. `gnrflex` performs the first stage of the estimation routine which returns the flexible input elasticity. `gnrflex` performs the second stage of the estimation routine which returns the fixed input elasticities and productivity.

An example of the use of `gnrprod`:

```{r}
require(gnrprod)

# load Colombian plant-level data
data <- colombian

# estimate production function parameters and productivity
gnr_fit <- gnrprod(output = "RGO", fixed = c("L", "K"), flex = "RI",
                   share = "share", id = "id", time = "year", data = data,
                   degree = 3, markov_degree = 3)

# print estimates
gnr_fit
summary(gnr_fit)
```

Alternatively, one can use `gnrflex` and `gnriv`:

```{r}
# estimate first stage
gnr_fs <- gnrflex(output = "RGO", fixed = c("L", "K"), flex = "RI",
                  share = "share", id = "id", time = "year", data = data,
                  degree = 3)

# print estimate
gnr_fs

# estimate second stage
gnr_ss <- gnriv(object = gnr_fs, degree = 3)

# print estimates
gnr_ss
```


## References

Gandhi, Amit, Salvador Navarro, and David Rivers. 2020. "On the Identification of Gross Output Production Functions." *Journal of Political Economy*, 128(8): 2973-3016. https://doi.org/10.1086/707736.


